Atypical Lyman-$\alpha$ emission in a dwarf galaxy via multiphase gas and rotation.

### 2017-01-16 paper/letter.tex
Fixed Max' name
mnras style

\documentclass[a4paper, usenatbib, 12pt]{article}
\usepackage{subfig}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{cite}
\usepackage[icelandic,spanish,english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[top=3.5cm, bottom=2.5cm, left=3.5cm,right=3.5cm]{geometry}

%----------------------New commands -------------------

\newcommand{\tol}{Tololo 1214-277}
\newcommand{\lya}{Ly$\alpha$}
\newcommand{\hb}{H$\beta$}
\newcommand{\ha}{H$\alpha$}
\newcommand{\oiii}{[OIII]}
\newcommand{\oii}{[OII]}
\newcommand{\nii}{[NII]}
\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
\newcommand{\es}{erg s$^{-1}$}
\newcommand{\esa}{erg s$^{-1}$}
\newcommand{\kms}{km s$^{-1}$}
\newcommand{\apj}{ApJ}  
\newcommand{\jcap}{JCAP}  
\newcommand{\apjs}{ApJS}  
\newcommand{\pasa}{PASA}  
\newcommand{\apjl}{ApJL}  
\newcommand{\aj}{AJ}  
\newcommand{\mnras}{MNRAS}  
\newcommand{\mnrassub}{MNRAS accepted}  
\newcommand{\aap}{A\&A}  
\newcommand{\aaps}{A\&AS}  
\newcommand{\araa}{ARA\&A}  
\newcommand{\nat}{Nature}  
\newcommand{\physrep}{PhR}
\newcommand{\pasp}{PASP}    
\newcommand{\pasj}{PASJ}    
\newcommand{\sigmaclump}{$54.3\pm 0.6$ km s$^{-1}$}
\newcommand{\inftyclump}{$54.3\pm 5.1$ km s$^{-1}$}
\newcommand{\probaclump}{$0.96\pm 0.01$}
\def\simgt{\lower.5ex\hbox{\gtsima}}
\def\simlt{\lower.5ex\hbox{\ltsima}}
%------------------------------------------------------

\begin{document}
\pagestyle{empty}
\noindent
\textbf{Line Traces of a Supermassive Dwarf Galaxy}
\\
\\
Jaime E. Forero-Romero$^{1}$, Max Groenke$^2$, Mar\'ia Camila
Remolina-Guti\'errez$^1$, Juan Nicol\'as
Garavito-Carmargo$^3$, Mark Dijkstra$^2$.
\\
\\
\scriptsize
{$^1$ Departamento de Física, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia 
\\
$^2$ Institute of Theoretical Astrophysics, University of Oslo,
Postboks 1029 Blindern, NO-0315 Oslo, Norway.
\\
$^3$ Department of Astronomy, University of Arizona, 933 North Cherry
Avenue, Tucson, AZ 85721, USA. 
\normalsize
\\
\\
\textbf{
  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe.    
Before the observational detection of the first galaxies becomes
reality, CDGs are the best systems to test our ideas on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad symmetric Lyman-$\alpha$ line emission that had evaded theoretical
interpretation so far. 
In this letter we explain these features by two different models: an
homogeneous gaseous sphere undergoing bulk rotation and an interstellar
medium composed by outflowing clumps with additional random motions.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these physical conditions.
We find that both models independently require high velocities
(either a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$ or a clump velocity
dispersion of \sigmaclump with outflows of
\inftyclump) consistent with a dynamical mass of at
least a billion solar masses, ten times larger than its baryonic mass.   
We argue that a possible explanation for this excess of
dynamical mass is the presence of a supermassive black hole at the
center of \tol. 
This work demonstrates the importance of considering multiphase
physics and rotation among the possible conditions shaping the
\lya\ spectra of the first galaxies.  
Additionally, if future kinematic maps of \tol\ confirm the high
velocities postulated in our model, it would provide new
evidence for dwarf galaxies as hosts of supermassive black
holes.  
}

@@

Almost fifty years ago \cite{PartridgePeebles} it was realized that
young galaxies could be detected through a strong Lyman-$\alpha$ line
emission.  
This theoretical prediction was only confirmed thirty years later on
distant, relatively young, not primordial, galaxies \cite{1998ApJ...498L..93D}.
Currently Lyman Alpha Emitting (LAE) galaxies are commonly targeted
in surveys. 
The presence of the Ly-$\alpha$ emission line provides confirmation of
the distance of a galaxy while provides clues about the stellar
population and inter-stellar medium conditions regulating the
Ly-$\alpha$ emission.

The Ly-$\alpha$ emission line is not exclusive of distant galaxies. 
Any galaxy with low dust content and ongoing star formation has the
right conditions to show this line.  
There are, for instance,  local Universe surveys that target
Ly-$\alpha$ emission in nearby dwarf star forming galaxies 
\cite{LARS}. 
The study of nearby LAE samples has allowed the study of other
indicators that might be more difficult to obtain for distant galaxies
such as morphology, dust attenuation, neutral hydrogen contents and
ionization state.

However, the physical interpretation of Ly-$\alpha$ observations is
not straightforward \cite{2015ApJ...805...14R}. 
This is due to the resonant nature of the Ly-$\alpha$ line. 
A Ly-$\alpha$ photon follows a diffusion-like process before escaping
the galaxy or being absorbed by dust. 
The resulting line profile becomes sensitive to the dynamical, chemical
and thermal conditions in the interstellar medium. 
There are very few analytically tools available to interpret the
emerging Ly-$\alpha$ line.
They are applicable only in very few cases of highly symmetrical
conditions, which are hardly met in real astrophysical systems.
For these reasons the interpretation of Ly-$\alpha$ observations
requires state-of-the-art Monte Carlo radiative transfer simulations.

\tol\ is a compact star forming dwarf galaxy that presents a
strong Ly-$\alpha$ emission \cite{Thuan97} with two puzzling 
features: the line is symmetric and single peaked.
Usually the Ly-$\alpha$ line has an asymmetric single or double peak. 
These two special features in \tol\ cannot be explained with
conventional models \cite{2006A&A...460..397V,2015ApJ...812..123G}.

In this letter we show how the \tol's \lya\ profile can be explained
either by rotation \cite{GaravitoCamargo2014} or the recently developed
class of more complex 
multiphase models that predict a wider variety of spectra
including, single, double and triply peaked spectra \cite{Gronke2016}.  
Figure 1. summarizes our findings.
Dots represent the observational data for \tol\ with the
overplot from our best fits from the analytical solution for a
rotating homogeneous gas sphere (thin line) and the multiphase
model (thick line). 
This is the first time that these models have been introduced with
success to explain an observed \lya\ profile.

@@

\tol's stellar mass is  $M_{\star} = 1.45\pm0.45\times 10^{8}
M_{\odot}$   \cite{2014PASP..126.1079M} and its total neutral HI mass is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$
\cite{pustilnikmartin07}; the dynamical mass is at least 12 to 160 times
the baryonic mass, depending if one considers the multiphase or
rotation estimate.

We lean towards the lower dynamical mass estimate from the multiphase
model as it seems easier to reconcile with the following two
astrophysical mechanisms for its origin.
The first way to explain a dynamical mass of $10^{9} M_{\odot}$
in a sphere of 2.25 kpc in radius, could be a dark matter halo of at
least $10^{12}$ M$_{\odot}$ in mass \cite{2011ApJ...726..108T}, which
leaves open the question as to why  \tol\ is not more similar to the
Milky Way galaxy as it would be hosted by a dark matter halo of similar
mass. 
A second possibility is that \tol\ hosts a supermassive black hole of
$10^{9} M_{\odot}$. This is almost two orders of magnitude higher
than the supermassive black hole found in the compact dwarf galaxy
M60-UCD1 \cite{2014Natur.513..398S}, which has a similar stellar mass
as \tol. This would leave open the question about the formation
process of such a system.

Another perspective to appreciate the atypically high dynamical mass
estimates comes from the observed scaling relations for dwarf
galaxies.
Assuming that \tol\ followed the fundamental plane relationship
between its mean surface brightness $I_e$, the projected half-light
radius $R_e$ and the velocity dispersion $\sigma$, described by $\log
I_e=1.6 \log\sigma - 1.21\log R_e + 0.55$ \cite{2009ApJ...698.1590G},
the expected velocity dispersion should be on the order of $5 \pm 1$ 
\kms, which is a factor of $\sim$ $10$ - $60$ lower than the 
results from the multiphase and rotation models, respectively. 
These are equivalent to factors of $\sim$ $100$ - $3600$ on the
dynamical mass.
Once again,  \tol\ seems to be significantly more massive than
expected.

A new observational test is needed to clarify the physical nature of
\tol. 
We suggest that integral field unit measurements spatially
resolving its spatial extent are up to the task. 
\tol\ spans a region of $4$ arcseconds,
an instrument such as the Multi Unit Spectroscopic Explorer
\cite{2014Msngr.157...13B} with its
nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
in wide-field mode could provide a coarse mapping of different
ionization lines to infer a kinematic map.
Another observational test includes the measurement of the
\lya\ ionizing continuum escape fraction.
In the rotational model this fraction should be zero, while
the multiphase model predicts that averaging over all sightlines
it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
variations depending on viewing angle \cite{2014MNRAS.444.1095G}.

All in all, the mere existence of a strong LAE galaxy with a broad,
symmetric line is interesting.
It raises the question whether some high redshift LAEs have asymmetric
lines because the blue half was truncated by the intergalactic medium.
In this case the \lya\ radiation could emerge as a low surface
brightness glow, which may be connected to \lya\ halos, while also
influencing the way LAEs can be used as a probe of reionization
\cite{2014PASA...31...40D}.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{CLARA-TOL-main.pdf}
\caption{{\bf Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.}
  Dots correspond to the observational data. The line shows the results
of our best model from a full radiative transfer simulation both for
the rotation and multiphase models.} 
\end{center}
\end{figure}

\bibliography{references}{}
\bibliographystyle{ieeetr}

\newpage

@@

\begin{table}
\begin{center}
\begin{tabular}{lc}
$\alpha$(2000)$^{a}$ & 12h17min17.1s\\
$\delta$(2000)$^{b}$ & -28d02m32s\\
$l$, $b$ (deg) & 294, 34\\
$m_V$ & 17.5\\
  M$_V$ & -17.6\\ 
$v$(km s$^{-1}$) & 7795\\
Ly-$\alpha$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
Ly-$\alpha$ EW & $70$\AA\\
H$\beta$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$) & $1.62\times 10^{-14}$ \\
$21$cm (Jy km s$^{-1}$)& $<0.10$ \\
\end{tabular}
\end{center}
\caption{Basic observational characteristics of TOL1214-277
  \cite{Thuan97}\\} 
\end{table}

\tol\ receding velocity is $7785\pm 50$km s$^{-1}$, which translates
into a distance of $106.6$ Mpc (with the Hubble constant $H_{0}$=73
Mpc km s$^{-1}$) 
Its metallicity is $\sim Z_{\odot}/24$ \cite{Izotov04} as derived from optical
spectroscopy.

The observed flux for the Lyman alpha line is $\sim
8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \cite{Thuan97}
and a Equivalent Width of $70$\AA\ and its H$\beta$ flux is 
$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
\cite{Izotov04} which gives a Ly$\alpha$/H$\beta$ flux ratio of
4.9$\pm$0.1. The Ly-$\alpha$ flux values correspond to luminosities of
$L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$ over a $20$\AA\ 
bandwidth, which in turns translates  into a star formation rate of
$2.0$ M$_{\odot}$ yr$^{-1}$ using a standard conversion factor between
luminosity and star formation rate of $9.1\times 10^{-43}$
$L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$. 
The absolute magnitude in the $V$ band translates into a luminosity of
$8.9\times 10^{8}$ L$_{\odot}$.
% using http://tomdwelly.com/tools_fluxtolum.php
Comparing this ratio with the theoretical expectation from case B
recombination of $23.3$ \cite{Hummer1987} one can estimate an escape
fraction of $20$\% for Ly$\alpha$ radiation.
The bolometric UV luminosity is $9.43\pm1.94 \times 10^{8}$
L$_{\odot}$ as measured by GALEX.

There is an upper limit for the  
integrated flux of $<0.10$ Jy km s$^{-1}$, which translates into a
upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$
\cite{pustilnikmartin07}.

The near-infrared fluxes at $3.6$ $\mu$m and $4.5$ $\mu$m are
$7.71\pm0.55\times 10^{-5}$ Jy and $7.98\pm0.71\times 10^{-5}$ Jy
\cite{2008ApJ...678..804E}.  Using a conversion between fluxes and
stellar mass calibrated on the Large Magellanic Cloud $M_{\star} =
10^{5.65} \times F_{3.6}^{2.85} \times F_{4.5}^{-1.85} \times
(D/0.05)^2 M_{\odot}$, where fluxes are in Jy and $D$ is the luminosity
distance to the source in Mpc, we find $M_{\star} = 1.45\pm0.45\times 10^{8}
M_{\odot}$, with a $30\%$ uncertainty coming from the calibration
process \cite{2012AJ....143..139E}.

We computed the projected half-luminosity radius to be $R_s=1.5\pm0.1$ kpc 
from the surface intensity profiles reported by.
\cite{2003A&A...410..481N}. 
Assuming spherical geometry, one can translate this value into a 3D
half-luminosity radius of $r_s=3R_s/2=2.25$ kpc.

@@

The rotation model corresponds to the work presented in
\cite{GaravitoCamargo2014} based on the Monte Carlo code
\texttt{CLARA} \cite{CLARA}. 
In that model the Ly-$\alpha$ photons are propagated 
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation.
The sphere is fully characterized by three parameters: the HI line's
center optical  depth $\tau$ measured from the center to its surface, the HI
temperature $T$, and the linear surface velocity $V_{\rm max}$.  
Photons are emitted at their natural frequency from the center of the
sphere. 
Including the effect of dust only changes the overall line
normalization but not its shape.  
The results we report in the main body of the paper do not include any
dust model.
In this letter we use an analytical solution that captures the most
important effects of rotation onto the \lya\ line.

@@

\cite{GaravitoCamargo2014} derived a concise analytical description for
those features. 
This description takes into account how different parts of the
sphere's surface shift in frequency the \lya\ photons. 
Different shifts in frequency come from different values for the projected
velocity along the LOS. 
Using the analytical solution for the \lya\ spectra of a static sphere
plus the right frequency shifts  computed from geometrical
considerations, one is able to compute an analytical solution for the
rotating sphere that reproduces the main features found using the full
numerical simulation.

The analytical solution for the rotation sphere was the base to
perform the Markov Chain Monte Carlo (MCMC) calculation using the
\texttt{emcee} Python library \cite{2013PASP..125..306F}. \texttt{emcee} 
is an open source optimized implementation of the affine-invariant 
ensemble sampler for MCMC. The algorithm creates a number of walkers that,
during a sufficient number of steps, generate parameters' combinations for
a specific model. For each time, the code calculates the likelihood of the
combination with respect to the observational data. The walkers ecplore
the parameter space sampling the likelihood function.

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.0\textwidth]{emcee_results.pdf}
\caption{{\bf Results from the Markov Chain Monte Carlo computation for
    the rotation model.} The dotted vertical lines in the outer histograms 
	represent the 16th, 50th and 84th percentiles. \label{emceeresults}} 
\end{center}
\end{figure}

@@

>>>>

\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e} 
%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage {graphicx}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{caption}
%Non reposionated tables
\usepackage{float}
\restylefloat{table}
%Multiple columns support for tables
\usepackage{array}
\usepackage{booktabs}
\setlength{\heavyrulewidth}{1.5pt}
\setlength{\abovetopsep}{4pt}

%=========================================================================
%		INTERNAL MACROS
%=========================================================================
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

% To highlight comments 
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
\newcommand{\before}[1]{\textcolor{red}{ #1}}
\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}

\newcommand{\tol}{Tololo 1214-277}
\newcommand{\lya}{Ly$\alpha$}
\newcommand{\hb}{H$\beta$}
\newcommand{\ha}{H$\alpha$}
\newcommand{\oiii}{[OIII]}
\newcommand{\oii}{[OII]}
\newcommand{\nii}{[NII]}
\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
\newcommand{\es}{erg s$^{-1}$}
\newcommand{\esa}{erg s$^{-1}$}
\newcommand{\kms}{km s$^{-1}$}
\newcommand{\apj}{ApJ}  
\newcommand{\jcap}{JCAP}  
\newcommand{\apjs}{ApJS}  
\newcommand{\pasa}{PASA}  
\newcommand{\apjl}{ApJL}  
\newcommand{\aj}{AJ}  
\newcommand{\mnras}{MNRAS}  
\newcommand{\mnrassub}{MNRAS accepted}  
\newcommand{\aap}{A\&A}  
\newcommand{\aaps}{A\&AS}  
\newcommand{\araa}{ARA\&A}  
\newcommand{\nat}{Nature}  
\newcommand{\physrep}{PhR}
\newcommand{\pasp}{PASP}    
\newcommand{\pasj}{PASJ}    
\newcommand{\sigmaclump}{$54.3\pm 0.6$ km s$^{-1}$}
\newcommand{\inftyclump}{$54.3\pm 5.1$ km s$^{-1}$}
\newcommand{\probaclump}{$0.96\pm 0.01$}
\def\simgt{\lower.5ex\hbox{\gtsima}}
\def\simlt{\lower.5ex\hbox{\ltsima}}

\begin{document}

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[Atypical Dwarf LAE]{
Atypical Lyman-$\alpha$ emission in a dwarf galaxy via multiphase
gas and rotation.}
\author[J.E. Forero-Romero et al.]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Max Gronke$^2$, 
Mar\'ia Camila Remolina-Guti\'errez$^1$,
\newauthor
Nicol\'as Garavito-Camargo$^3$, 
Mark Dijkstra$^2$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
$^2$ Institute of Theoretical Astrophysics, University of Oslo,
Postboks 1029 Blindern, NO-0315 Oslo, Norway.\\
$^3$ Department of Astronomy, University of Arizona, 933 North Cherry
Avenue, Tucson, AZ 85721, USA. 
}

%\vspace*{6pt}\\

%}
\maketitle

\begin{abstract}
Example.
\end{abstract}

\begin{keywords}
Methods: data analysis - numerical 
\end{keywords}

%=========================================================================
%		PAPER CONTENT
%=========================================================================

%*************************************************************************
\section{Introduction}
\label{sec:introduction}

  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe.    
Before the observational detection of the first galaxies becomes
reality, CDGs are the best systems to test our ideas on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad symmetric Lyman-$\alpha$ line emission that had evaded theoretical
interpretation so far. 
In this letter we explain these features by two different models: an
homogeneous gaseous sphere undergoing bulk rotation and an interstellar
medium composed by outflowing clumps with additional random motions.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these physical conditions.
We find that both models independently require high velocities
(either a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$ or a clump velocity
dispersion of \sigmaclump with outflows of
\inftyclump) consistent with a dynamical mass of at
least a billion solar masses, ten times larger than its baryonic mass.   
We argue that a possible explanation for this excess of
dynamical mass is the presence of a supermassive black hole at the
center of \tol. 
This work demonstrates the importance of considering multiphase
physics and rotation among the possible conditions shaping the
\lya\ spectra of the first galaxies.  
Additionally, if future kinematic maps of \tol\ confirm the high
velocities postulated in our model, it would provide new
evidence for dwarf galaxies as hosts of supermassive black
holes.

@@

Almost fifty years ago \citep{PartridgePeebles} it was realized that
young galaxies could be detected through a strong Lyman-$\alpha$ line
emission.

This theoretical prediction was only confirmed thirty years later on
distant, relatively young, not primordial, galaxies \citep{1998ApJ...498L..93D}.
Currently Lyman Alpha Emitting (LAE) galaxies are commonly targeted
in surveys. 
The presence of the Ly-$\alpha$ emission line provides confirmation of
the distance of a galaxy while provides clues about the stellar
population and inter-stellar medium conditions regulating the
Ly-$\alpha$ emission.

The Ly-$\alpha$ emission line is not exclusive of distant galaxies. 
Any galaxy with low dust content and ongoing star formation has the
right conditions to show this line.  
There are, for instance,  local Universe surveys that target
Ly-$\alpha$ emission in nearby dwarf star forming galaxies 
\citep{LARS}. 
The study of nearby LAE samples has allowed the study of other
indicators that might be more difficult to obtain for distant galaxies
such as morphology, dust attenuation, neutral hydrogen contents and
ionization state.

However, the physical interpretation of Ly-$\alpha$ observations is
not straightforward \citep{2015ApJ...805...14R}. 
This is due to the resonant nature of the Ly-$\alpha$ line. 
A Ly-$\alpha$ photon follows a diffusion-like process before escaping
the galaxy or being absorbed by dust. 
The resulting line profile becomes sensitive to the dynamical, chemical
and thermal conditions in the interstellar medium. 
There are very few analytically tools available to interpret the
emerging Ly-$\alpha$ line.
They are applicable only in very few cases of highly symmetrical
conditions, which are hardly met in real astrophysical systems.
For these reasons the interpretation of Ly-$\alpha$ observations
requires state-of-the-art Monte Carlo radiative transfer simulations.

\tol\ is a compact star forming dwarf galaxy that presents a
strong Ly-$\alpha$ emission \citep{Thuan97} with two puzzling 
features: the line is symmetric and single peaked.
Usually the Ly-$\alpha$ line has an asymmetric single or double peak. 
These two special features in \tol\ cannot be explained with
conventional models \citep{2006A&A...460..397V,2015ApJ...812..123G}.

In this letter we show how the \tol's \lya\ profile can be explained
either by rotation \citep{GaravitoCamargo2014} or the recently developed
class of more complex 
multiphase models that predict a wider variety of spectra
including, single, double and triply peaked spectra \citep{Gronke2016}.  
Figure 1. summarizes our findings.
Dots represent the observational data for \tol\ with the
overplot from our best fits from the analytical solution for a
rotating homogeneous gas sphere (thin line) and the multiphase
model (thick line). 
This is the first time that these models have been introduced with
success to explain an observed \lya\ profile.

@@

\tol's stellar mass is  $M_{\star} = 1.45\pm0.45\times 10^{8}
M_{\odot}$   \citep{2014PASP..126.1079M} and its total neutral HI mass is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$
\citep{pustilnikmartin07}; the dynamical mass is at least 12 to 160 times
the baryonic mass, depending if one considers the multiphase or
rotation estimate.

We lean towards the lower dynamical mass estimate from the multiphase
model as it seems easier to reconcile with the following two
astrophysical mechanisms for its origin.
The first way to explain a dynamical mass of $10^{9} M_{\odot}$
in a sphere of 2.25 kpc in radius, could be a dark matter halo of at
least $10^{12}$ M$_{\odot}$ in mass \citep{2011ApJ...726..108T}, which
leaves open the question as to why  \tol\ is not more similar to the
Milky Way galaxy as it would be hosted by a dark matter halo of similar
mass. 
A second possibility is that \tol\ hosts a supermassive black hole of
$10^{9} M_{\odot}$. This is almost two orders of magnitude higher
than the supermassive black hole found in the compact dwarf galaxy
M60-UCD1 \citep{2014Natur.513..398S}, which has a similar stellar mass
as \tol. This would leave open the question about the formation
process of such a system.

Another perspective to appreciate the atypically high dynamical mass
estimates comes from the observed scaling relations for dwarf
galaxies.
Assuming that \tol\ followed the fundamental plane relationship
between its mean surface brightness $I_e$, the projected half-light
radius $R_e$ and the velocity dispersion $\sigma$, described by $\log
I_e=1.6 \log\sigma - 1.21\log R_e + 0.55$ \citep{2009ApJ...698.1590G},
the expected velocity dispersion should be on the order of $5 \pm 1$ 
\kms, which is a factor of $\sim$ $10$ - $60$ lower than the 
results from the multiphase and rotation models, respectively. 
These are equivalent to factors of $\sim$ $100$ - $3600$ on the
dynamical mass.
Once again,  \tol\ seems to be significantly more massive than
expected.

A new observational test is needed to clarify the physical nature of
\tol. 
We suggest that integral field unit measurements spatially
resolving its spatial extent are up to the task. 
\tol\ spans a region of $4$ arcseconds,
an instrument such as the Multi Unit Spectroscopic Explorer
\citep{2014Msngr.157...13B} with its
nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
in wide-field mode could provide a coarse mapping of different
ionization lines to infer a kinematic map.
Another observational test includes the measurement of the
\lya\ ionizing continuum escape fraction.
In the rotational model this fraction should be zero, while
the multiphase model predicts that averaging over all sightlines
it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
variations depending on viewing angle \citep{2014MNRAS.444.1095G}.

All in all, the mere existence of a strong LAE galaxy with a broad,
symmetric line is interesting.
It raises the question whether some high redshift LAEs have asymmetric
lines because the blue half was truncated by the intergalactic medium.
In this case the \lya\ radiation could emerge as a low surface
brightness glow, which may be connected to \lya\ halos, while also
influencing the way LAEs can be used as a probe of reionization
\citep{2014PASA...31...40D}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{CLARA-TOL-main.pdf}
\caption{{\bf Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.}
  Dots correspond to the observational data. The line shows the results
of our best model from a full radiative transfer simulation both for
the rotation and multiphase models.} 
\end{center}
\end{figure*}

@@

\begin{table}
\begin{center}
\begin{tabular}{lc}
$\alpha$(2000)$^{a}$ & 12h17min17.1s\\
$\delta$(2000)$^{b}$ & -28d02m32s\\
$l$, $b$ (deg) & 294, 34\\
$m_V$ & 17.5\\
  M$_V$ & -17.6\\ 
$v$(km s$^{-1}$) & 7795\\
Ly-$\alpha$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
Ly-$\alpha$ EW & $70$\AA\\
H$\beta$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$) & $1.62\times 10^{-14}$ \\
$21$cm (Jy km s$^{-1}$)& $<0.10$ \\
\end{tabular}
\end{center}
\caption{Basic observational characteristics of TOL1214-277
  \citep{Thuan97}\\} 
\end{table}

\tol\ receding velocity is $7785\pm 50$km s$^{-1}$, which translates
into a distance of $106.6$ Mpc (with the Hubble constant $H_{0}$=73
Mpc km s$^{-1}$) 
Its metallicity is $\sim Z_{\odot}/24$ \citep{Izotov04} as derived from optical
spectroscopy.

The observed flux for the Lyman alpha line is $\sim
8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}
and a Equivalent Width of $70$\AA\ and its H$\beta$ flux is 
$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
\citep{Izotov04} which gives a Ly$\alpha$/H$\beta$ flux ratio of
4.9$\pm$0.1. The Ly-$\alpha$ flux values correspond to luminosities of
$L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$ over a $20$\AA\ 
bandwidth, which in turns translates  into a star formation rate of
$2.0$ M$_{\odot}$ yr$^{-1}$ using a standard conversion factor between
luminosity and star formation rate of $9.1\times 10^{-43}$
$L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$. 
The absolute magnitude in the $V$ band translates into a luminosity of
$8.9\times 10^{8}$ L$_{\odot}$.
% using http://tomdwelly.com/tools_fluxtolum.php
Comparing this ratio with the theoretical expectation from case B
recombination of $23.3$ \citep{Hummer1987} one can estimate an escape
fraction of $20$\% for Ly$\alpha$ radiation.
The bolometric UV luminosity is $9.43\pm1.94 \times 10^{8}$
L$_{\odot}$ as measured by GALEX.

There is an upper limit for the  
integrated flux of $<0.10$ Jy km s$^{-1}$, which translates into a
upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$
\citep{pustilnikmartin07}.

The near-infrared fluxes at $3.6$ $\mu$m and $4.5$ $\mu$m are
$7.71\pm0.55\times 10^{-5}$ Jy and $7.98\pm0.71\times 10^{-5}$ Jy
\citep{2008ApJ...678..804E}.  Using a conversion between fluxes and
stellar mass calibrated on the Large Magellanic Cloud $M_{\star} =
10^{5.65} \times F_{3.6}^{2.85} \times F_{4.5}^{-1.85} \times
(D/0.05)^2 M_{\odot}$, where fluxes are in Jy and $D$ is the luminosity
distance to the source in Mpc, we find $M_{\star} = 1.45\pm0.45\times 10^{8}
M_{\odot}$, with a $30\%$ uncertainty coming from the calibration
process \citep{2012AJ....143..139E}.

We computed the projected half-luminosity radius to be $R_s=1.5\pm0.1$ kpc 
from the surface intensity profiles reported by.
\citep{2003A&A...410..481N}. 
Assuming spherical geometry, one can translate this value into a 3D
half-luminosity radius of $r_s=3R_s/2=2.25$ kpc.

@@

The rotation model corresponds to the work presented in
\citep{GaravitoCamargo2014} based on the Monte Carlo code
\texttt{CLARA} \citep{CLARA}. 
In that model the Ly-$\alpha$ photons are propagated 
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation.
The sphere is fully characterized by three parameters: the HI line's
center optical  depth $\tau$ measured from the center to its surface, the HI
temperature $T$, and the linear surface velocity $V_{\rm max}$.  
Photons are emitted at their natural frequency from the center of the
sphere. 
Including the effect of dust only changes the overall line
normalization but not its shape.  
The results we report in the main body of the paper do not include any
dust model.
In this letter we use an analytical solution that captures the most
important effects of rotation onto the \lya\ line.

@@

\citep{GaravitoCamargo2014} derived a concise analytical description for
those features. 
This description takes into account how different parts of the
sphere's surface shift in frequency the \lya\ photons. 
Different shifts in frequency come from different values for the projected
velocity along the LOS. 
Using the analytical solution for the \lya\ spectra of a static sphere
plus the right frequency shifts  computed from geometrical
considerations, one is able to compute an analytical solution for the
rotating sphere that reproduces the main features found using the full
numerical simulation.

The analytical solution for the rotation sphere was the base to
perform the Markov Chain Monte Carlo (MCMC) calculation using the
\texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
is an open source optimized implementation of the affine-invariant 
ensemble sampler for MCMC. The algorithm creates a number of walkers that,
during a sufficient number of steps, generate parameters' combinations for
a specific model. For each time, the code calculates the likelihood of the
combination with respect to the observational data. The walkers ecplore
the parameter space sampling the likelihood function.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{emcee_results.pdf}
\caption{{\bf Results from the Markov Chain Monte Carlo computation for
    the rotation model.} The dotted vertical lines in the outer histograms 
	represent the 16th, 50th and 84th percentiles. \label{emceeresults}} 
\end{center}
\end{figure*}

@@

\bibliographystyle{mn2e}
\bibliography{references}
